Electronic polarizability as the fundamental variable in the dielectric properties of two-dimensional materials

### 2019-03-14 paper.tex
Correct minor typo
Apply changes locally

nuclei) to the static $\varepsilon$ is considered.

@@

electron cloud \cite{Israelachvili_2011}).

>>>>

nuclei) to the static $\varepsilon$ is not considered.

@@

electron cloud \cite{Israelachvili_2011}). We also note that such
approach is essentially different from the effective medium theory
(EMT) treatment\cite{Aspnes_1982} of 2D materials, in which the
hypothetical effective dielectric constant of 2D materials
$\varepsilon_{\mathrm{2D}}$ are extracted from the macroscopic
dielectric constant \cite{Matthes_2016,Laturia_2018}, from
pre-determined 2D layer thickness $\delta$. The 2D electronic
polarizability approach solves the issue of overestimation in the EMT
approach, and $\alpha_{\mathrm{2D}}$ has an umambiguous physical
meaning. Detailed discussions can be found in Supplementary Section
\ref{SI-sec:2D-3D-rescale}.
